%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------------------------------------------------
%                   Header
%----------------------------------------------------
\begin{center}
  \textbf{\Huge \scshape Chenyu Gu} \\ \vspace{3pt}
  \small
  \faMobile \hspace{.5pt} \href{tel:14046374484}{+1 (404) 637 4484}
  $|$
  \faAt \hspace{.5pt} \href{mailto:cgu84@gatech.edu}{cgu84@gatech.edu}
  $|$
  \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Georgia+Institute+of+Technology/@33.7756222,-84.3988599,16z/data=!3m1!4b1}{Atlanta, United States}
\end{center}

%----------------------------------------------------
%                  Education
%----------------------------------------------------
\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Georgia Institute of Technology}{Atlanta, United States}
{M.
  S.
  in Bioengineering (ECE); \textbf{GPA: 4.00/4.00}}{Aug 2024 -- Present}
\resumeItem{\small \textbf{Relevant coursework:}
  Digital Control System, Finite Element Analysis.
}

\resumeSubheading
{Southern University of Science and Technology}{Shenzhen, China}
{B.
  S.
  in Intelligent Medical Engineering; \textbf{GPA: 3.82/4.00}}{Aug 2020 -- Jun 2024}
\resumeItem{\small \textbf{Relevant coursework:}
  Medical Robotics, Principles of Electrical Circuits, Signals and Systems, Digital Signal
  Processing, Medical Imaging, Machine Learning, Neural Engineering, BCI.
}

\resumeSubheading
{KTH Royal Institute of Technology}{Stockholm, Sweden}
{Exchange student in Electrical Engineering and Computer Science}{Sep 2023 -- Jan 2024}
\resumeItem{\small \textbf{Relevant coursework:}
  Principles of Wireless Sensor Networks, Social Robotics.
}

\resumeSubheading
{Imperial College London}{London, United Kingdom}
{Data Science Bachelor Summer School; \textbf{Grade: B-merit}}{Jun 2022 -- Aug 2022}

\resumeSubHeadingListEnd

%----------------------------------------------------
%               Research Interests
%----------------------------------------------------
\section{Research Interests}
\vspace{2pt}
\textbf{Medical Robotics, Wearable Technology, Human Movement, and Medical Devices.}

%----------------------------------------------------
%                 Publications
%----------------------------------------------------
\section{Publicatios}
\vspace{3pt}
\resumeItemListStart
  \resumeItem{
    \textbf{C. Gu} et al., “IMU-based motion capture system for rehabilitation applications: A systematic
    review,” \textit{Biomimetic Intelligence and Robotics}, vol. 3, no. 2, p. 100097, 2023. DOI: \href{https://doi.org/10.1016/j.birob.2023.100097}{10.1016/j.birob.2023.100097}.
  }
  \resumeItem{
  \textbf{C. Gu} et al., "A Portable Inertial Navigation System for Total Hip Arthroplasty Targeting Direct Anterior Approach," in \textit{IEEE Transactions on Instrumentation and Measurement}, doi: 10.1109/TIM.2025.3548784.
  }
\resumeItemListEnd

%----------------------------------------------------
%                 Publications
%----------------------------------------------------
\section{Patents}
\vspace{3pt}
\resumeItemListStart
  \resumeItem{
Li Guangheng, Zhang Mingming, Yu Yangyi, and \textbf{Gu Chenyu}. A joint replacement simulation device and a joint replacement simulation method. China CN118634071A, filed July 9, 2024, and issued September 13, 2024. https://patents.google.com/patent/CN118634071A/en?oq=CN118634071A.
  }
  \resumeItem{
    Zhang Mingming, and \textbf{Gu Chenyu}. Human motion capture method, system and storage medium. China CN118870291A, filed July 9, 2024, and issued October 29, 2024. https://patents.google.com/patent/CN118870291A.
  }
\resumeItemListEnd

%----------------------------------------------------
%                 Experience
%----------------------------------------------------
\section{Experience}
\vspace{3pt}
\resumeSubHeadingListStart

%---------- Hydraulic Tendon Driven Guidewire ----------
\resumeSubheading
{Hydraulic Tendon Driven Guidewire}{Atlanta, United States}
{Project Leader in RoboMed Lab}{Oct 2024 -- Present}
\resumeItemListStart
\resumeItem{Designed a hydraulic tendon-driven guidewire that is non-conductive, MRI safe, and steerable in 3D.}
\resumeItem{Modeled both static and kinematic properties of the guidewire and conducted experiments to verify the model.}
\resumeItemListEnd

%---------- Movement Analysis ----------
\resumeSubheading
{Movement Analysis using IMU Sensors}{Stockholm, Sweden}
{Visiting Student in Intelligent Heart Technology Lab (I-HeaL)}{Oct 2023 -- Jan 2024}
\resumeItemListStart
\resumeItem{Extracted gait parameters and human center of mass to explore the relationship between human movement and cardiovascular function.}
\resumeItem{Deployed a Kalman filter for orientation estimation, calibrated IMU angles, and developed algorithms for gait/COM extraction.}
\resumeItemListEnd

%---------- Motion Capture for Rehabilitation ----------
\resumeSubheading
{Motion Capture for Rehabilitation}{Shenzhen, China}
{Project Leader in Brain-robot Rehabilitation Lab}{Apr 2022 -- May 2024}
\resumeItemListStart
\resumeItem{Integrated UWB technology and IMU to develop a motion capture system for human motion recovery.}
\resumeItem{Developed Unity visualization and Python code for signal transmission.
  Applied deep learning for sparse motion capture.
}
\resumeItem{Evaluated the system’s effectiveness on healthy subjects during rehabilitation exercises.}
\resumeItemListEnd

%---------- Navigation System for Surgeries ----------
\resumeSubheading
{Navigation System for Surgeries}{Shenzhen, China}
{Project Leader in Brain-robot Rehabilitation Lab}{Feb 2022 -- Oct 2023}
\resumeItemListStart
\resumeItem{Designed a surgery navigation system with on-handle and on-body modules, integrating a 9-axis IMU and gyroscope.}
\resumeItem{Demonstrated the system’s effectiveness for total hip arthroplasty surgeries via the direct anterior approach.}
\resumeItemListEnd

%---------- Center of Mass Estimation ----------
\resumeSubheading
{Center of Mass Estimation and Rehabilitation Applications}{Shenzhen, China}
{Project Assistant in Brain-robot Rehabilitation Lab}{Oct 2022 -- Aug 2023}
\resumeItemListStart
\resumeItem{Used IMU-based motion capture to estimate the 3D center of mass for rehabilitation applications.}
\resumeItem{Analyzed the center of mass to extract motion features and perform rehabilitation assessments.}
\resumeItemListEnd

%---------- Review on Motion Capture for Rehabilitation ----------
\resumeSubheading
{Review on Motion Capture for Rehabilitation}{Shenzhen, China}
{Researcher in Brain-robot Rehabilitation Lab}{Jun 2022 -- Oct 2022}
\resumeItemListStart
\resumeItem{Investigated current IMU-based motion capture technology for rehabilitation and authored a comprehensive review.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------------------------------------------------
%                   Projects
%----------------------------------------------------
\section{Projects}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Design a Prototype of a Cardiopulmonary Resuscitation Robot}{Course Project \textbf{Grade: A}}
{Project Leader}{Apr 2023 -- May 2023}
\resumeItemListStart
\resumeItem{Designed a prototype medical robot for cardiopulmonary resuscitation.}
\resumeItem{Completed 3D modeling of the drone robot in SolidWorks and developed the robot's kinematic/control flow.}
\resumeItemListEnd

\resumeSubheading
{Road Network Visualization of Taxi Data}{Course Project \textbf{Grade: A}}
{Project Leader}{May 2023 -- Apr 2023}
\resumeItemListStart
\resumeItem{Visualized Shenzhen taxi data and performed data analysis (origin-destination, density).}
\resumeItem{Cleaned large-scale data, extracted relevant features, and proposed urban construction improvements based on findings.}
\resumeItemListEnd

\resumeSubheading
{Word Representation in Biomedical Domain}{Summer School \textbf{Grade: B}}
{Project Assistant, Imperial College London}{Jul 2022 -- Aug 2022}
\resumeItemListStart
\resumeItem{Developed a deep learning model for word representation in the medical field using n-gram, skip-gram, and t-SNE for visualization.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------------------------------------------------
%             Awards & Achievements
%----------------------------------------------------
\section{Awards \& Achievements}
\vspace{2pt}
\small{
  \begin{tabular}{p{16.3cm}@{\extracolsep{\fill}}r}
    \textbf{(School-level) Excellent Graduation Thesis Award}                               & Jul 2024         \\[3pt]
    \textbf{(School-level) Outstanding Student Scholarship of Zhicheng College}             & 2021, 2022, 2023 \\[3pt]
    \textbf{(Provincial-level) "Internet Plus" Innovation and Entrepreneurship Competition} & Aug 2023         \\[3pt]
    \textbf{(School-level) "Internet Plus" Innovation and Entrepreneurship Competition}     & Jul 2022         \\[3pt]
    \textbf{(School-level) Excellent Team of "Sycamore Tree" Competition}                   & May 2022         \\[3pt]
    \textbf{(National-level) RoboMaster 2021 Mecha Master Super Competition (First Prize)}  & Sep 2021         \\[3pt]
    \textbf{(Top 3 in the Major) "Fu Turui" Fellowship, Dept. of Biomedical Engineering}    & Oct 2021         \\[3pt]
    \textbf{(Top 4 in the Province) First Prize Scholarship for Freshmen}                   & Sep 2020
  \end{tabular}
}

%----------------------------------------------------
%                     Skills
%----------------------------------------------------
\section{Skills}
\vspace{3pt}
\resumeItemListStart
\resumeItem{\textbf{Laboratory:} 3D printing, PCB design, Soldering, Oscilloscope, Signal generator,
  Motion capture system, Force plate.}
\resumeItem{\textbf{Programming:}
  Python (data analysis, ML), C (embedded), MATLAB (analysis), Rust (systems), Java.
}
\resumeItem{\textbf{Software:}
  SolidWorks (3D modeling), JLC-EDA (PCB design), Unity (game interface), Blender.
}
\resumeItem{\textbf{Tools:}
  Git, Neovim, Docker, Jupyter, VS Code, Microsoft Office.
}
\resumeItemListEnd

%----------------------------------------------------
%            Extracurricular Activities
%----------------------------------------------------
\section{Extracurricular Activities}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{South University of Science and Technology Archery Team}{Oct 2020 -- Oct 2021}
{Member of School Archery Team}{Shenzhen, China}
\resumeItem{Joined the school archery team and organized training/competitions.}

\resumeSubheading
{Student Union of Zhicheng College}{Sep 2020 -- Jun 2021}
{Member, Propaganda Department}{Shenzhen, China}
\resumeItem{Organized various campus events, including the New Year's Eve party and “Nanke Voice.”}

\resumeSubHeadingListEnd

%----------------------------------------------------
%                    Languages
%----------------------------------------------------
\section{Languages}
\vspace{3pt}
\resumeItemListStart
\resumeItem{\textbf{Chinese:} Native speaker}
\resumeItem{\textbf{English:} Fluent (TOEFL: 100)}
\resumeItem{\textbf{Japanese and German:} Elementary}
\resumeItemListEnd

\end{document}
