%-------------------------
% Resume in LaTeX
% Author: Chenyu Gu
%-------------------------

\documentclass[letterpaper,10pt]{article}

%----------------------------------------------------
%                  Packages
%----------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}        % for symbols like \Letter
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}     % for GitHub, LinkedIn icons, etc.
\usepackage{makecell}        % for multi-line cells in tables
\input{glyphtounicode}       % ensure PDF is ATS-friendly

% Ensure generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%----------------------------------------------------
%                 Page Setup
%----------------------------------------------------
\pagestyle{fancy}
\fancyhf{}               % clear all header and footer fields
\fancyfoot{}             % no page numbering
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

% URL style
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

%----------------------------------------------------
%          Custom Commands for Resume
%----------------------------------------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[5]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \multicolumn{2}{l}{\textit{\small#5}}\\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small#3}
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{
  \item[$\circ$] \small\textbf{{#1 \vspace{-4pt}}}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% For itemized lists with custom indentation
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%                RESUME START
%-------------------------------------------
\begin{document}

%----------------------------------------------------
%                     Header
%----------------------------------------------------
\begin{center}
  \textbf{\Huge \scshape Chenyu Gu} \\ \vspace{3pt}
  \small
  \faMobile \hspace{.5pt} \href{tel:14046374484}{+1 (404) 637 4484}
  $|$
  \faAt \hspace{.5pt} \href{mailto:cgu84@gatech.edu}{cgu84@gatech.edu}
  $|$
  \faLinkedinSquare \hspace{.5pt}\href{https://www.linkedin.com/in/chenyu-gu-38337226b/}{LinkedIn}
\end{center}

%----------------------------------------------------
%                   Education
%----------------------------------------------------
\vspace{-20pt}
\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{Georgia Institute of Technology}{Atlanta, United States}
{M.
  S.
  in Bioengineering (ECE); \textbf{GPA: 4.00/4.00}}{Aug 2024 -- Present}
{\textbf{Relevant coursework:}
  Finite Element Method, Robotics, Digital Control, ML.
}

\vspace{-3pt}
\resumeEducationHeading
{Southern University of Science and Technology}{Shenzhen, China}
{B.
  S.
  in Intelligent Medical Engineering; \textbf{GPA: 3.82/4.00}}{Aug 2020 -- Jun 2024}
{\small
  \makecell[{{p{0.97\textwidth}}}]{%
    \textbf{Achievements:}
    Excellent Graduation Thesis Award, Outstanding Student Scholarship, First Prize of Scholarship for
    Freshmen.
    \\
    \textbf{Relevant coursework:}
    Medical Robotics \& Imaging, Circuits, Digital Signal Processing, Neural Engineering and BCI.
    \vspace{5pt}
  }
}

\vspace{-7pt}
\resumeEducationHeading
{KTH Royal Institute of Technology}{Stockholm, Sweden}
{Exchange student in Electrical Engineering and Computer Science}{Sep 2023 -- Jan 2024}
{\textbf{Relevant coursework:}
  Principles of Wireless Sensor Networks, Social Robotics.
}

\vspace{-3pt}
\resumeEducationHeading
{Imperial College London}{London, United Kingdom}
{Data Science Bachelor Summer School; \textbf{Grade: B-merit}}{Jun 2022 -- Aug 2022}
{\textbf{Relevant coursework:}
  Deep Learning.
}

\resumeSubHeadingListEnd

%----------------------------------------------------
%                     Skills
%----------------------------------------------------
\section{Skills}
\vspace{3pt}
\resumeItemListStart

\resumeItem{\textbf{Laboratory:}
  FEM analysis, 3D printing, PCB design, Soldering, Oscilloscope, Signal generator, Motion capture
  system.
}

\resumeItem{\textbf{Programming:}
  Python (Proficient in data analysis and ML), C (Embedded systems), MATLAB (Data analysis), Rust
  (Systems design), Java.
}

\resumeItem{\textbf{Software:}
  Ansys (FEM), SolidWorks (3D modeling), EasyEDA/KiCad (PCB design), Unity (Game interface), Blender.
}

\resumeItem{\textbf{Tools:}
  Git, Neovim, Docker, Jupyter, VS Code, Adobe PS, Final Cut Pro, Microsoft Office.
}

\resumeItemListEnd

%----------------------------------------------------
%                  Experience
%----------------------------------------------------
\vspace{-8pt}
\section{Experience}
\vspace{3pt}
\resumeSubHeadingListStart

%---------- RoboMed Lab ----------
\resumeSubheading
{RoboMed Lab}{Atlanta, United States}
{Graduate Research Assistant; \textbf{Skills:}
  \textbf{CAD Modeling \& PCB Design, Robotics Modeling \& Control}}{Oct 2024 -- Present} \resumeItemListStart
\resumeItem{Designed a hydraulic tendon-driven guidewire that is non-conductive, MRI safe, and
  steerable in 3D.
}
\resumeItem{Modeled static and kinematic properties of the guidewire and conducted experiments to validate the model.}
\resumeItemListEnd

%---------- I-HeaL Lab ----------
\resumeSubheading
{Intelligent Heart Technology Lab (I-HeaL)}{Stockholm, Sweden}
{Visiting Research Assistant; \textbf{Skills:}
  \textbf{Algorithm Development, Signal Processing}}{Oct 2023 -- Jan 2024} \resumeItemListStart
\resumeItem{Extracted gait parameters and human COM to explore the relationship between movement
  and cardiovascular functions.
}
\resumeItem{Deployed a Kalman filter for IMU sensor and developed algorithms for gait and COM extraction.}
\resumeItemListEnd

%---------- Dept. of Orthopedics ----------
\resumeSubheading
{Department of Orthopedics, First People's Hospital}{Shenzhen, China}
{Research Assistant; \textbf{Skills:}
  \textbf{Embedded Systems (HW \& SW), Clinical Validation}}{Jun 2023} \resumeItemListStart
\resumeItem{Developed a surgery navigation system using on-handle and on-body modules with a 9-axis
  IMU and gyroscope.
}
\resumeItem{Demonstrated effectiveness in total hip arthroplasty surgeries via the direct anterior approach.}
\resumeItemListEnd

%---------- Rehab Center ----------
\resumeSubheading
{Rehabilitation Center, Second People's Hospital}{Shenzhen, China}
{Intern; \textbf{Skills:}
  \textbf{Clinical Trails, Patient Interaction}}{Aug 2022} \resumeItemListStart \resumeItem{Assisted
  doctors in rehabilitation evaluations and facility setup for patient rehabilitation.
}
\resumeItem{Acquired familiarity with basic rehabilitation facilities and procedures.}
\resumeItemListEnd

%---------- Brain-robot Rehabilitation Lab ----------
\resumeSubheading
{Brain-robot Rehabilitation Lab}{Shenzhen, China}
{Project Leader, Undergraduate Research Assistant}{Feb 2022 -- May 2024}
\resumeItemListStart

\resumeSubItem{Motion Capture for Rehabilitation; \textit{Skills: System Development, Deep Learning}}
\resumeItem{Developed a motion capture system using UWB technology and IMU for human motion recovery.}
\resumeItem{Created Unity visualization and Python code for signal transmission.
  Applied deep learning for sparse motion capture.
}
\resumeItem{Tested on healthy subjects for rehabilitation exercises and evaluated effectiveness.}

\resumeSubItem{Center of Mass Estimation and Rehabilitation Applications; \textit{Skills: Data Analysis, Acquisition}}
\resumeItem{Utilized IMU motion capture to estimate 3D human center of mass for rehabilitation purposes.}
\resumeItem{Analyzed the center of mass to extract motion features and perform rehabilitation assessments.}

\resumeSubItem{Review on Motion Capture for Rehabilitation; \textit{Skills: Literature Review}}
\resumeItem{Investigated IMU-based motion capture applications in rehabilitation and authored a comprehensive review.}

\resumeItemListEnd

\resumeSubHeadingListEnd

%----------------------------------------------------
%                 Publications
%----------------------------------------------------
\vspace{-12pt}
\section{Publications}
\resumeItemListStart
\resumeItem{
  \textbf{C.
    Gu*} et al., “IMU-based motion capture system for rehabilitation applications: A systematic
  review,” \textit{Biomimetic Intelligence and Robotics}, vol.
  3, no. 2, p. 100097, 2023.
  DOI: \href{https://doi.org/10.1016/j.birob.2023.100097}{10.1016/j.birob.2023.100097}.
  (2023 Best Paper Award)
}
\resumeItem{
  \textbf{C.
    Gu} et al., "A Portable Inertial Navigation System for Total Hip Arthroplasty Targeting Direct
  Anterior Approach," in IEEE Transactions on Instrumentation and Measurement, vol.
  74, pp. 1-13, 2025, Art no. 4004013, doi: \href{https://doi.org/10.1109/TIM.2025.3548784}{10.1109/TIM.2025.3548784}.
}
\resumeItemListEnd

%----------------------------------------------------
%                 Misc
%----------------------------------------------------
\vspace{-8pt}
\section{Extracurricular \& Misc}
\resumeItemListStart
\resumeItem{\textbf{Language:}
  English (Proficient), Chinese (Proficient), French (Elementary).
}
\resumeItem{\textbf{Involvement:}
  Member of the propaganda department of student union, Member of school archery team.
}
\resumeItemListEnd

\end{document}
